Manuscript for MADA Project

### 2023-04-27 products/Manuscript.qmd
NG Review Added

# Summary
This study aims to conduct a secondary analysis of residents of the black community in Albany, GA that have received at least one dose of the COVID-19 vaccine from September 2022 through February 2023 and live in the one of the three zip codes 31701, 31705 and 31707. The outcome of interest is the difference in vaccination rates by month from September through February. The predictor of interest is the presence of a COVID-19 Vaccine Hesitancy Program Intervention.

@@

## General Background
Back in March 2020, COVID-19 greatly impacted the citizens of the Albany, GA. Early on in the COVID-19 pandemic Albany, GA was ranked the "forth-worst" city hit by COVID-19 in the United States [@Rapier2020]. According to U.S Census Bureau, 74.5% of the total population of the City of Albany is made up by residents that are black. In a study that examined the health outcomes of residents who tested positive for COVID-19 in Albany, GA it was found that 83.3% of 710 patients that were hospitalized for COVID-19 were black[@Racine2022]. Although there was no differences in hospital mortality found between residents that were black compared to residents that were not black but there was a much higher percentage of hospitalizations due to COVID-19 for residents who were black.

@@

### Zip code 31701
The vaccination rate of the the Black population slightly decreased from a rate of 61% to 60.6% \@ref(fig:31701_total_black_vax_rate). The vaccination rate for female black residents slightly decreased from 65% to 64% while the male black resident population's vaccination rate increased slightly at 53% to 57%. It is important to note the difference between the vaccination rates of female and male black residents, which is around .1 from September to February \@ref(fig:31701_Gender_black_vax). When the black population was stratified by age, the rates were the highest for the ages of 65 and older at 89%. Black residents aged 45-64 had a steady rate of 70%, black residents aged 18-44 had a steady rate of 65%, blacked residents aged 10-17 had a steady rate of 40% and black residents aged 5-9 had a steady rate of 12% \@ref(fig:31701_Age_black_vax).

@@

### Zip code 31705
The vaccination rate of stayed stable around 48% for the black population in the 31705 zip code \@ref(fig:31701_Age_black_vax). The vaccination rate of female black residents dropped from 51.1% to 49.7% from September to December, but remained stable close to 50% until February. For male black residents the vaccination rate hovered around 44% \@ref(fig:31705_Gender_black_vax). After stratifying by age the vaccination rates for the 65+, 44-64, 18-44, 10-17 and 5-9 ages groups were as follows: 85%, 68%, 43%, 35% and 12% \@ref(fig:31705_Age_black_vax).

@@

### Zip code 31707
The total vaccination rate of black residents in the 31707 zip code was around 50% from September through February \@ref(fig:31707_total_black_vax_rate). The vaccination rates for the female and male black population were found to be steady around 54% and 44% \@ref(fig:31707_Gender_black_vax). The vaccination rates by the age groups 65+, 44-64, 18-44, 10-17 and 5-9 where found to be 98%, 85%, 52%, 37%, and 17% \@ref(fig:31707_Age_black_vax).

@@

### Zip code 30815
The total vaccination rate for the black population was 44% in the 30815 zip code from September through February \@ref(fig:30815_total_black_vax_rate). The vaccination rates for black female and male residents were 49% and 38% \@ref(fig:30815_Gender_black_vax). The vaccination rates by the age groups 65+, 44-64, 18-44, 10-17 and 5-9 where found to be 78%, 60%, 38%, 31%, and 8% \@ref(fig:30815_Age_black_vax).

@@

### Zip code 30907
The total vaccination rate for the black population was 54% in September and dropped to around 53% in February in the 30907 zip code \@ref(fig:30907_total_black_vax_rate). The vaccination rates for black female and male residents were 60% and 45% \@ref(fig:30907_Gender_black_vax). The vaccination rates by the age groups 65+, 44-64, 18-44, 10-17 and 5-9 where found to be 95%, 64%, 63%, 33%, and 11% \@ref(fig:30907_Age_black_vax).

@@

# Discussion
Albany, Georgia is predominately black

>>>>

# Summary

This study aims to conduct a secondary analysis of residents of the black community in Albany, GA that have received at least one dose of the COVID-19 vaccine from September 2022 through February 2023 and live in the one of the three zip codes 31701, 31705 and 31707. The outcome of interest is the difference in vaccination rates by month from September through February. The predictor of interest is the presence of a COVID-19 Vaccine Hesitancy Program Intervention.

@@

## General Background

Back in March 2020, COVID-19 greatly impacted the citizens of the Albany, GA. Early on in the COVID-19 pandemic Albany, GA was ranked the "forth-worst" city hit by COVID-19 in the United States [@Rapier2020]. According to U.S Census Bureau, 74.5% of the total population of the City of Albany is made up by residents that are black. In a study that examined the health outcomes of residents who tested positive for COVID-19 in Albany, GA it was found that 83.3% of 710 patients that were hospitalized for COVID-19 were black[@Racine2022]. Although there was no differences in hospital mortality found between residents that were black compared to residents that were not black but there was a much higher percentage of hospitalizations due to COVID-19 for residents who were black.

@@

### Zip code 31701

The vaccination rate of the the Black population slightly decreased from a rate of 61% to 60.6% \@ref(fig:31701_total_black_vax_rate). The vaccination rate for female black residents slightly decreased from 65% to 64% while the male black resident population's vaccination rate increased slightly at 53% to 57%. It is important to note the difference between the vaccination rates of female and male black residents, which is around .1 from September to February \@ref(fig:31701_Gender_black_vax). When the black population was stratified by age, the rates were the highest for the ages of 65 and older at 89%. Black residents aged 45-64 had a steady rate of 70%, black residents aged 18-44 had a steady rate of 65%, blacked residents aged 10-17 had a steady rate of 40% and black residents aged 5-9 had a steady rate of 12% \@ref(fig:31701_Age_black_vax).

@@

### Zip code 31705

The vaccination rate of stayed stable around 48% for the black population in the 31705 zip code \@ref(fig:31701_Age_black_vax). The vaccination rate of female black residents dropped from 51.1% to 49.7% from September to December, but remained stable close to 50% until February. For male black residents the vaccination rate hovered around 44% \@ref(fig:31705_Gender_black_vax). After stratifying by age the vaccination rates for the 65+, 44-64, 18-44, 10-17 and 5-9 ages groups were as follows: 85%, 68%, 43%, 35% and 12% \@ref(fig:31705_Age_black_vax).

@@

### Zip code 31707

The total vaccination rate of black residents in the 31707 zip code was around 50% from September through February \@ref(fig:31707_total_black_vax_rate). The vaccination rates for the female and male black population were found to be steady around 54% and 44% \@ref(fig:31707_Gender_black_vax). The vaccination rates by the age groups 65+, 44-64, 18-44, 10-17 and 5-9 where found to be 98%, 85%, 52%, 37%, and 17% \@ref(fig:31707_Age_black_vax).

@@

### Zip code 30815

The total vaccination rate for the black population was 44% in the 30815 zip code from September through February \@ref(fig:30815_total_black_vax_rate). The vaccination rates for black female and male residents were 49% and 38% \@ref(fig:30815_Gender_black_vax). The vaccination rates by the age groups 65+, 44-64, 18-44, 10-17 and 5-9 where found to be 78%, 60%, 38%, 31%, and 8% \@ref(fig:30815_Age_black_vax).

@@

### Zip code 30907

The total vaccination rate for the black population was 54% in September and dropped to around 53% in February in the 30907 zip code \@ref(fig:30907_total_black_vax_rate). The vaccination rates for black female and male residents were 60% and 45% \@ref(fig:30907_Gender_black_vax). The vaccination rates by the age groups 65+, 44-64, 18-44, 10-17 and 5-9 where found to be 95%, 64%, 63%, 33%, and 11% \@ref(fig:30907_Age_black_vax).

@@

# Discussion

Albany, Georgia is predominately black
